
\documentclass{article} % For LaTeX2e
\usepackage{iclr2026_conference,times}

% Optional math commands from https://github.com/goodfeli/dlbook_notation.
% \input{math_commands.tex}

\usepackage{booktabs}
\usepackage{array}
\usepackage{graphicx}  % for \resizebox

\usepackage{caption}
\usepackage{amsmath,amsfonts,bm}
% Required packages for the theorem
\usepackage{amsthm}      % For theorem, proof, and remark environments
\usepackage{amssymb}     % For 

% Optional but recommended
\usepackage{mathtools}   % Extends amsmath with 
\usepackage{algorithm}
\usepackage[algo2e, linesnumbered, ruled, vlined]{algorithm2e}
\usepackage{algpseudocode}

\usepackage{wrapfig}             
\usepackage{lipsum} 

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section] 
\newtheorem{remark}{Remark}[section]
\newtheorem{proposition}{Proposition}[section]

\newcommand{\mc}[1]{\mathcal{#1}}  % Shortcut for \mathcal
\newcommand{\mbf}[1]{\mathbf{#1}}  % Shortcut for \mathbf
\newcommand{\mbb}[1]{\mathbb{#1}}  % Shortcut for \mathbb
\newcommand{\tsc}[1]{\textsc{#1}}  
\newcommand{\ttt}[1]{\texttt{#1}}  

\usepackage{hyperref}       % hyperlinks
\hypersetup{
    colorlinks = true,
    citecolor = [HTML]{0668E1},  
    linkcolor  = [HTML]{8B0000},  % DarkRed
    filecolor  = [HTML]{00008B},  % DarkBlue
    urlcolor   = [HTML]{00008B}   % DarkBlue
}

\usepackage{twemojis} 
\usepackage{fontawesome5}

\usepackage{url}
\usepackage{tcolorbox}

\usepackage{multirow}
\usepackage[table]{xcolor}
\definecolor{mybrown}{HTML}{EA580C}
\definecolor{mygreen}{HTML}{008744}
\definecolor{myorange}{HTML}{ffa700}
\definecolor{myred}{HTML}{d62d20}
\usepackage{subcaption}
\DeclareMathOperator*{\argmax}{arg\,max}

\usepackage{makecell}
\usepackage{xcolor} 
\usepackage{subcaption} % in preamble

\usepackage{natbib}

\input{macros.tex}


\title{Predicting LLM Reasoning Performance with Small Proxy Model}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

\author{
  Woosung Koh\textsuperscript{$\triangledown$\scalebox{0.85}{$\spadesuit$}}, 
  Juyoung Suk\textsuperscript{$\triangledown\scalebox{0.85}{$\spadesuit$}$}, 
  Sungjun Han\textsuperscript{$\triangledown\star$}, 
  Se-Young Yun\textsuperscript{\scalebox{0.85}{$\spadesuit$}$\star$},
  Jamin Shin\textsuperscript{$\triangledown \star$}\\
  \textsuperscript{$\triangledown$}Trillion Labs, \textsuperscript{\scalebox{0.85}{$\spadesuit$}}KAIST AI\\
  \footnotesize{\textsuperscript{$\star$}Correspondence to: yunseyoung@kaist.ac.kr, \{sungjun.han, jay\}@trillionlabs.co}
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

% \preprintcopy
\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}


\maketitle

\input{sections/0_abstract} 
\input{sections/1_intro}
\input{sections/2_problem}
\input{sections/3_method}
\input{sections/4_results}
\input{sections/5_discussion}

\newpage
\section{Ethics Statement} \label{app:ethic}
Our work conforms to the ICLR Code of Ethics. We report minor use of LLMs for polishing writing. All LLM-generated content has been reviewed and verified by the authors, who take full responsibility for the accuracy and integrity of the work presented.

\section{Reproducibility Statement} \label{app:reproduce}
Our method \tsc{rBridge} is fully reproducible using the information provided in this paper. The approach follows a straightforward process: applying a specific prompt to a frontier model, then computing our proposed negative log-likelihood as presented in Eq. (\ref{eq:rbridge_nll}) and illustrated in Fig. \ref{fig:rbridge}. We provide the exact prompt in  Appendix \ref{app:pseudocode} along with pseudocode (Alg. \ref{alg:rbridge}) for implementation. To further support reproducibility and benefit the research community, we open-sourced our dataset.

\section{Acknowledgment} 
This research was fully funded by Trillion Labs. Se-Young Yun was partially supported by the Institute of Information \& communications Technology Planning \& Evaluation (IITP) grant funded by the Korea government (MSIT) (No. 2022-0-00871, Development of AI Autonomy and Knowledge Enhancement for AI Agent Collaboration).

\bibliography{iclr2025_conference}
\bibliographystyle{iclr2025_conference}

\newpage
\appendix
\input{sections/7_appendix}

\end{document}
